\section{Scenario based design} \label{sec:scenario_based_design}
Useful in all four stages of the Y-model (section \ref{sec:y_model}), scenarios and personas are one of the most fundamental and popular techniques to designing interactive systems. \cite[p. 62]{benyon14}

\input{part1/definitions/scenario_user_story.tex}
\input{part1/definitions/scenario_conceptual_scenario.tex}
\input{part1/definitions/scenario_concrete_scenario.tex}
\input{part1/definitions/scenario_use_case.tex}

A central tool used in the scenario based design is also the \emph{persona}, which can especially enhance both concrete scenarios and use cases and in parts also conceptual scenarios and for revising user stories

\input{part1/definitions/persona.tex}

With all four types of scenarios we see all activities of the Y-model are covered. Many user stories show the users needs of the system, abstracted into very few conceptual scenarios defining the vision for the solution. These few then create many concrete scenarios generating concrete solutions, from them many more use cases specifying the exact details of the functions of the system. This relation between the stories, the design process and the Y-model is visualized in figure \ref{fig:scenarios}. \cite[p. 66, 196]{benyon14}

\input{part1/figures/scenarios.tex}

\input{part1/definitions/scenario_corpus.tex}

While the PACT framework of section \ref{sec:pact} is used to critique the scenarios, the fast growing amount of scenarios needs to be managed. To help collaboration and conveying the point of the scenarios they can be annotated with a description of the personas included, the activities covered, and the key points of the scenario among other things. These descriptions can be further annotated with meta data, such as the author of and their rationale for the scenario, its changehistory, and the domains to which it generalizes. Furthermore how the scenarios are related to eachother, such as what scenario spawned another, can be very valuable \cite[p. 70,72]{benyon14}

\input{part1/definitions/endnote.tex}
\input{part1/definitions/trade-offs_and_claims.tex}
\input{part1/definitions/object_action.tex}

Together all of this can be used to derive the conceptual model and design language of section \ref{sec:conceptual_model}, and from method \ref{meth:object-action_analysis} can tool \ref{tool:conceptual_model} be derived. \cite[p. 67]{benyon14}
